Vagueness and imprecise imitation in signaling games

### 2016-02-25 paper/version_05/paper.tex
Rephrased Lipman's reference for clarity. Small changes in second to last paragraph of Section 2.1. Wrote some possible replies to the reviewers.

But there are other intriguing aspects about vagueness. One perplexing issue is how vagueness
could arise and be maintained in the first place. This is an apparent puzzle for functionalist
accounts that maintain that concepts and linguistic meanings evolved driven towards
efficiency. Since the existence of unclear borderline cases seems to entail inefficiency of
categorization or communication, the challenge, succinctly put forward by
\citet{Lipman2009:Why-is-Language}, is to explain two things at the same time: (i) how
vagueness can persist under evolutionary pressure to be optimally discriminative, (ii) without
jeopardizing the possibility of evolving, learning and communicating with a meaningful
language. A number of authors have consequently tried to explain why vagueness evolved as
something that is itself useful
\citep[e.g.][]{Jaegherde-Jaegher2003:A-Game-Theoreti,Deemter2009:Utility-and-Lan,BlumeBoard2013:Intentional-Vag}.
Others have argued that vagueness is a natural byproduct of limitations in information
processing \citep[e.g.][]{FrankeJager2010:Vagueness-Signa} or of generalization in low-level
learning strategies \citep[e.g.][]{OConnor2013:The-Evolution-o}. This paper contributes to the
latter line of thought.

@@

It is intuitive to think that linguistic and conceptual categories are orderly in such a
manner.  For example, if you consider two people, one with a height of 2m and another with a
height of 2.2m, both `tall', it would be difficult to defend considering a person with a height
of 2.1m `short'.  Another example is that of color categorization. The World Color Survey
project~\citep{CookKay2005:The-World-Color,WCS} collected color naming data for 110 unwritten
languages of 45 language families.  For the great majority of these languages a pattern can be
observed: basic color terms are by and large convex~\citep{Regier07,Jager2010}. A prominent
school of thought in comparative linguistics also assumes that more abstract conceptual domains
---e.g., spatial-topological relations, temporal reference, or the meanings expressible by
indefinite pronouns--- are preferably carved up by the languages of the world in such a way
that meanings are connected regions on a so-called \emph{semantic map}
\citep[e.g.][]{Croft2003:Typology-and-Un,Haspelmath2003:The-geometry-of,LevinsonMeira2003:Natural-concept}. It
is premature to argue that these observations can be extended to \emph{all} cases of
categorization. However, for the cases where it does apply, the result of
\citet{JagerMetzger2011:Voronoi-Languag} is interesting because it demonstrates that signaling
can impose this kind of orderly categories on a metric space without that being the ulterior
purpose of it all.%
\footnote{For the concrete case of color categorization, see also
  \citet{JagerRooijvan-Rooij2007:Language-Struct} and \citet{Correia2015}}

>>>>

But there are other intriguing aspects about vagueness. One perplexing issue is how vagueness
could arise and be maintained in the first place. This is an apparent puzzle for functionalist
accounts that maintain that concepts and linguistic meanings evolved driven towards
efficiency. \citet{Lipman2009:Why-is-Language} argues that, technically, the existence of unclear borderline cases always entails inefficiency of
categorization or communication. The challenge is then to explain how
vagueness can persist both: (i) under evolutionary pressure to be optimally discriminative, and (ii) without
jeopardizing the possibility of evolving, learning and communicating with a meaningful
language. A number of authors have consequently tried to explain why vagueness evolved as
something that is itself useful
\citep[e.g.][]{Jaegherde-Jaegher2003:A-Game-Theoreti,Deemter2009:Utility-and-Lan,BlumeBoard2013:Intentional-Vag}.
Others have argued that vagueness is a natural byproduct of limitations in information
processing \citep[e.g.][]{FrankeJager2010:Vagueness-Signa} or of generalization in low-level
learning strategies \citep[e.g.][]{OConnor2013:The-Evolution-o}. This paper contributes to the
latter line of thought.

@@

It is intuitive to think that linguistic and conceptual categories are orderly in such a
manner.  For example, if you consider two people `tall', one with a height of 2m and another with a
height of 2.2m, it would be difficult to defend not considering a person with a height
of 2.1m `tall' as well. Another example where this intuition is additionally supported by empirical data is that of color categorization. The World Color Survey
project~\citep{CookKay2005:The-World-Color,WCS} collected color naming data for 110 unwritten
languages of 45 language families.  For the great majority of these languages a pattern can be
observed: basic color terms are by and large convex~\citep{Regier07,Jager2010}. It
is premature to argue that these observations can be extended to \emph{all} cases of
categorization. However, for the cases where it does apply, the result of
\citet{JagerMetzger2011:Voronoi-Languag} is interesting because it demonstrates that signaling
can impose this kind of orderly categories on a metric space without that being the ulterior
purpose of it all.%
\footnote{For the concrete case of color categorization, see also
  \citet{JagerRooijvan-Rooij2007:Language-Struct} and \citet{Correia2015}}
Finally, these considerations are in line with a prominent
school of thought in comparative linguistics which also assumes that more abstract conceptual domains
(e.g., spatial-topological relations, temporal reference, or the meanings expressible by
indefinite pronouns) are preferably carved up by the languages of the world in such a way
that meanings are connected regions on a so-called \emph{semantic map}
\citep[e.g.][]{Croft2003:Typology-and-Un,Haspelmath2003:The-geometry-of,LevinsonMeira2003:Natural-concept}.
